---
title: "STATS 250: Homework 9"
author: "Homework Team"
date: "November 13, 2020"
output:
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    theme: lumen
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if (!require(checkmate))
  install.packages('checkmate')
source("plotT.R")
```

### Question 2
The data can be found in `decibel.csv`, and you will need to load it into RStudio. The instructions for this question can be found on course.work.

```{r Q2readIn, error = T}
# Replace this comment with your code or add it to the next line

```

```{r Q2conditionsCheck, error = T}
# Replace this comment with your code or add it to the next line

```

```{r Q2interval, error = T}
# Replace this comment with your code or add it to the next line

```

### Question 3
The data also uses the `decibel.csv` data that you read in for Question 2.

```{r Q3test, error = T}
# Replace this comment with your code or add it to the next line

```

### Extra spot for work
Here are a few extra chunks if you need it to work on hw09.

```{r hw09work1, error = T}
# Replace this comment with your code or add it to the next line

```

```{r hw09work2, error = T}
# Replace this comment with your code or add it to the next line

```

```{r hw09work3, error = T}
# Replace this comment with your code or add it to the next line

```

## Wrapping Up

Make sure that you submit the appropriate output from this RStudio Project to the corresponding questions on course.work.
